Analysis of survey data collected by CHILDREN for a better World e.V.

### 2020-02-28 paper.tex

the introduction should include: motivation, precise research questions, very short literature review, most important results, further proceedings

CHILDREN's aims for data analysis\\ 
CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany. We call them organizations in the following. They apply to CHILDREN for yearly grants. If approved, they are supposed to use them for specific purposes defined by CHILDREN. CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program). The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them. In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries. The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.  
Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.

\subsection{Literature overview}

Previous research shows, that the childhood and youth is central in development of character traits and future opportunities. Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life. Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance. Moreover, Deckers et. al. (2015) found by experiments in Germany, that children of higher educated parents are significantly more patient. Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions (Deckers et. al. 2015, Case et. al. 2002). Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves. This could have a negative influence on their character development. For example, Chetty et. al (2014) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions. Furthermore, the result of Deckers et. al. (2020) provides causal evidence on the effect of social environment on prosocial attitudes. Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions. Heckmann et. al. (2010) investigated a preschool education program in the US. He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.

\section{Data}

To measure the effect of CHILDREN´s engagement on the funded organizations, we use the data CHILDREN collected from 2011 to 2018. In each year they send a survey to the organizations with several questions about the previous year. The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020. In some organizations one employee fills in the survey and in others they do it as a team. Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees. The number of variables varies over time as well. Included are numbers such as the average eaters per meal or the amount of money they provide to the organizations but also general questions. For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization. This part of the survey must be answered on a scale from zero (no kids) to four (all kids). If an organization does not answer a question, this is documented as a “99”. We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions. The surveyed variables change over the years, but some of them are included every year. 
However, we did several steps to get a full dataset we could work with (we could use for our empirical analysis??). The data was divided into one dataset for each survey from 2011 to 2019, but we only use the surveys till 2018 since in 2019 some organization-ID´s occurred several times and the data for 2019 were incomplete. Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018. Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout. This makes a quick work with R possible since we only use paths relative to the working directory. Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions. We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years. Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on. To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name. As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected. For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards. The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno). 
Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section. 
The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year. The questions are divided in two categories: the variables regarding to the meals program, answered by all organizations since they are all part of this program and the trips program variables, answered by the organizations that take part on the trips program in the respective year. Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.

Many organizations do not answer all questions CHILDREN poses. We create a seperate data set, in which we impute missing values with an organization-specific linear trend. CHILDREN supports some very large organizations that give out hundreds of meals a day or conduct dozens of trips per year. We fit our models with outliers excluded to see if they are driving results. We define an outlier as a value that is at least 1.5 interquartile ranges below the 25th percentile or equally far above the 75th percentile. Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 23:08:35 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:09:02 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
  \label{lessIllOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:09:03 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
  \label{dietaryOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:09:04 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
  \label{appreciateOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:09:04 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
  \label{selfworthOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:09:05 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
  \label{dayToDayOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany. We call them organizations in the following. They apply to CHILDREN for yearly grants. If approved, they are supposed to use them for specific purposes defined by CHILDREN. CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program). The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them. In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries. The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.  
Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.

Previous research shows, that the childhood and youth is central in development of character traits and future opportunities. Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life. Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}. Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves. This could have a negative influence on their character development. For example, \textcite{Chetty.2014} investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions. Furthermore, the result of \textcite{Kosse.2020} provides causal evidence on the effect of social environment on prosocial attitudes. Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions. \textcite{Heckman.2010} investigated a preschool education program in the US. He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.

CHILDREN for a better World e.V. is a non-profit organization supporting social institutions for children and adolescents across Germany, such as youth centers. Their goal is to foster equality of opportunities for the youth in Germany. CHILDREN supports poor and disadvantaged families and young people in socially problematic areas. Furthermore, they fight child poverty and encourage the youth to engage in society. We call the institutions funded by CHILDREN organizations in the following. Organizations have to apply for funding from CHILDREN each year again. In the application process, CHILDREN requires the applicants to answer a survey which contains questions about outcomes related to CHILDREN’s programs as well as general information about the organization such as the yearly budget.
CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program). The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and adolescents that visit them. In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries. The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.

Previous research shows that childhood and youth are central in the development of character traits and future opportunities. Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life. Heckmann and Carneiro (2003) show that especially early family factors determine most of the gaps in high school attendance. Moreover, Deckers et. al. (2015) found, by experiments conducted in Germany, that children of higher educated parents are significantly more patient. Children from parents with lower income and a lower educational level typically have a lower weight at birth and are born in a later week of gestation, which are all indicators for bad initial conditions (Deckers et. al. 2015, Case et. al. 2002). Children that grow up in families with a low socio-economic status are often believed to be less mobile. This could have a negative influence on their character development. For example, Chetty et. al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions. Furthermore, the results of Deckers et. al. (2020) provide evidence for the effect of the social environment on prosocial attitudes. Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children. Heckmann et. al. (2010) investigated a preschool education program in the US. The authors show that an investment in the improvement of the childhood conditions could have a high rate of return, even after controlling for possible distortions.

The aim of our project paper is to test whether CHILDREN’s programs positively influence the beneficiaries. We look at the associations between the subsidy CHILDREN provides and the share of beneficiaries with broadened everyday expertise and improved selfworth. Furthermore, we analyze the association between the measure of the healthiness of the meals the organizations offer and health-relevant outcomes of beneficiaries. The aim of our applied differences-in-differences estimation is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
We find no profound connection between the subsidy CHILDREN provides and the effectiveness of the organizations regarding the share of beneficiaries with broadened everyday expertise and improved selfworth. On the other hand, focusing on health relevant variables, we obtain a positive association between the index of healthy diet criteria fulfilled by organizations and the share of beneficiaries who are less frequently ill. By using the differences-in-differences (DID) strategy, the estimates show that the participation in the trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries. Strikingly, we observe a negative association between participating in the trips program and selfworth. However, the results of the DID estimation should not be overstated because of the small sample size.
The remainder of this project paper is structured as follows: Section \ref{data} describes the variable used for the empirical analysis. Then we present summary statistics. We explain the dimensionality reducing method factor analysis. The proceeding section reports different regression results. After that, we implement the differences-in-differences strategy to test for the effects of the trips program. Finally, we conclude and provide suggestions for CHILDREN.

\section{Data}
\label{data}

To measure the effect of CHILDREN's programs on the supported organizations, we use data from 2011 to 2018. In each year CHILDREN sends a survey to the organizations with several questions about the previous year. The number of organizations varies across years and increases over time: From 52 organizations in 2011 to 68 organizations in 2018. In some organizations one specific employee answers the survey questions, while in other institutions the questionnaire is answered in a team. As the children and adolescents are not questioned directly, all responses are documented as perceptions of the employees. The constellation of the variables in the data set also varies across years. For instance, CHILDREN asks for the average amount of kids that increased their confidence or improved their dietary knowledge. These questions of the survey are based on a scale of five levels from no to all kids. We perform several steps to receive a full dataset, which we use in our empirical analysis. Originally, the data was divided into seperate data sets for the respective years. We only use the surveys until 2018, because in 2019 some organization-ID´s occurred multiple times and the dataset for 2019 was incomplete. To ensure comparability across years, we named all variables the same. We merged the different datasets to a common dataset, including all years and variables CHILDREN collected. For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards. The three variants are ordinal, standardized and weighted.
Furthermore, we created a set of new variables. For instance, we used the information CHILDREN gave us to assign the German states to the corresponding organization-ID. 
The final dataset for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year. The questions are divided in two categories. The first part of the data set includes variables regarding the meals program. The second part contains variables affecting the trips program. The final data set comprises the years 2011 to 2018.
Many organizations do not answer all questions CHILDREN poses. We create a seperate data set, in which we impute missing values with an organization-specific linear trend. CHILDREN supports some very large organizations that give out hundreds of meals a day or conduct dozens of trips per year. We fit our models with outliers excluded to see if they are driving results. We define an outlier as a value that is at least 1.5 interquartile ranges below the 25th percentile or equally far above the 75th percentile. Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 23:48:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:48:53 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
  \label{lessIllOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:48:54 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
  \label{dietaryOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:48:54 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
  \label{appreciateOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:48:55 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
  \label{selfworthOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:48:55 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
  \label{dayToDayOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
